# Reproducible Research: Peer Assessment 1



## Loading and preprocessing the data

The following code will set the correct working directory and then read the 
data into R using the Read CSV function:

```{r}
setwd("~/Repository/Coursera/RepData_PeerAssessment1")
data <- read.csv("activity.csv", header=TRUE)
```

## What is mean total number of steps taken per day?

The following code will calculate the number of Steps taken each day:

```{r}
stepsPerDay <- aggregate(formula=steps~date, data=data, FUN=sum, na.rm=TRUE)
```

The following code will construct a histogram of the total number of steps take
each day:

```{r}
hist(stepsPerDay$steps, xlab="Steps per Day", ylab="Frequency", 
    main="Frequency of Steps per Day")
```

The following code will calculate the mean and the median of the total number 
of steps taken each day:

```{r}
meanStepsPerDay <- mean(stepsPerDay$steps, na.rm=TRUE)
medianStepsPerDay <- median(stepsPerDay$steps, na.rm=TRUE)
```

## What is the average daily activity pattern?

The following code will create a time series plot which shows the average 
number of steps taken, averaged across all days by interval:

```{r}
averageStepsPerInterval <- aggregate(formula=steps~interval, data=data, 
    FUN=mean)
plot(averageStepsPerInterval, type="l", xlab="Interval", ylab="Average Daily
    Steps", main="Average Number of Steps by Interval")
```

The following code will show which 5-minute interval, on average across all 
days, contains the maximum number of steps:

```{r}
averageStepsPerInterval$interval[which.max(averageStepsPerInterval$steps)]
```

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?


