# Reproducible Research: Peer Assessment 1



## Loading and preprocessing the data

The following code will set the correct working directory and then read the 
data into R using the Read CSV function:

```{r}
setwd("~/Repository/Coursera/RepData_PeerAssessment1")
data <- read.csv("activity.csv", header=TRUE)
```

## What is mean total number of steps taken per day?

The following code will calculate the number of Steps taken each day:

```{r}
stepsPerDay <- aggregate(formula=steps~date, data=data, FUN=sum, na.rm=TRUE)
```

The following code will construct a histogram of the total number of steps take
each day:

```{r}
hist(stepsPerDay$steps, xlab="Steps per Day", ylab="Frequency", 
main="Frequency of Steps per Day")
```

The following code will calculate the mean and the median of the total number 
of steps taken each day:

```{r}
meanStepsPerDay <- mean(data$steps, na.rm=TRUE)
medianStepsPerDay <- median(data$steps, na.rm=TRUE)
```

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?


